A meta-analysis of mental rotation ability in the first years of life

### 2022-04-25 code/analysis.Rmd
Tune forest plot
- Make x axis symmetric
- Use long group IDs
- Split effect size + CI into 3 separate columns

# Compute standard error of Cohen's d based on assumed correlation
# See Hedges' formula on p. 253 in http://dx.doi.org/10.20982/tqmp.14.4.p242
# This will need a sensitivity analysis regarding the values of `r_assumed`
r_assumed <- 0.5
dat_all %>%
  mutate(
    ni = sample_size,
    vi = (dfi / (dfi - 2)) * ((2 * (1 - r_assumed)) / ni) *
      (1 + gi^2 * (ni / (2 * (1 - r_assumed)))) - (gi^2 / ji^2),
    sei = sqrt(vi)
  ) %>%
  filter(!is.na(gi)) %>%
  select(
    article,
    group,
    experiment,
    gender_split,
    gi,
    ni,
    vi,
    sei,
    female_percent,
    age_mean,
    age_sd,
    age_min,
    age_max,
    task
  ) -> dat_all_r

@@

# Create forest plot
dat %>%
  # Make sure the plot will be ordered alphabetically by experiment IDs
  arrange(experiment) %>%
  mutate(
    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
    # Show article labels only for the first experiment per article
    article = if_else(article == lag(article, default = ""), "", article),
    # Compute frequentist confidence intervals
    ci_lb = gi - qnorm(level / 2, lower.tail = FALSE) * sqrt(vi),
    ci_ub = gi + qnorm(level / 2, lower.tail = FALSE) * sqrt(vi),
    ci_print = print_ci(gi, ci_lb, ci_ub)
  ) %>%
  # Prepare plotting canvas
  ggplot(aes(x = gi, y = experiment_f)) +
  geom_vline(xintercept = seq(-1, 2, 1), size = 0.8, color = "grey90") +
  geom_vline(xintercept = seq(-1.5, 2.5, 1), size = 0.4, color = "grey90") +
  # Add article and group labels as text on the left
  geom_text(aes(x = -5.6, label = article), hjust = 0) +
  geom_text(aes(x = -3.1, label = group), hjust = 0) +
  # Add experiment-specific effect sizes and CIs as text on the right
  geom_text(aes(x = 4.4, label = ci_print), hjust = 1) +
  # Add Bayesian highest posterior density intervals for each experiment
  stat_interval(aes(x = .epred), draws, point_interval = "mean_hdi") +
  scale_color_grey(
    start = 0.9, end = 0.6,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  # Add experiment-specific effect sizes and CIs as dots with error bars
  geom_errorbar(aes(xmin = ci_lb, xmax = ci_ub)) +
  geom_point(aes(size = ni), shape = 15) + # Or (1 / vi)?
  # Add posterior distribution for the meta-analytic effect
  stat_halfeye(
    aes(x = b_Intercept, y = -1),
    meta_draws,
    point_interval = "mean_hdi"
  ) +
  annotate(
    "text",
    x = -5.6,
    y = -0.5,
    label = "Three-level model",
    hjust = 0,
    fontface = "bold"
  ) +
  annotate(
    "text",
    x = 4.4,
    y = -0.5,
    label = print_ci(
      meta_effect_size$Estimate,
      meta_effect_size$`l-95% CI`,
      meta_effect_size$`u-95% CI`
    ),
    hjust = 1,
    fontface = "bold"
  ) +
  # Add headers for each of the for columns
  annotate( # Just to make the grid lines disappear
    "rect",
    xmin = -Inf,
    xmax = Inf,
    ymin = n_experiments + 0.5,
    ymax = Inf,
    fill = "white"
  ) +
  annotate(
    "text",
    x = c(-5.6, -3.1, 0, 4.4),
    y = n_experiments + 1.5,
    label = c(
      "Article", "Experiment", "Effect size plot", "Effect size statistic"
    ),
    hjust = c(0, 0, 0.5, 1),
    fontface = "bold"
  ) +
  # Styling
  coord_cartesian(ylim = c(-1.5, n_experiments + 2), expand = FALSE) +
  scale_x_continuous(breaks = seq(-1.5, 2.5, 0.5)) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    size = "Sample size",
    color = "Bayesian HPDI"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.565),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica")
  )

# Save the plot
ggsave(here(figures_dir, "forest.pdf"), width = 9, height = 13)
```

>>>>

# Compute standard error of Cohen's d based on assumed correlation
# See Hedges' formula on p. 253 in http://dx.doi.org/10.20982/tqmp.14.4.p242
# This will need a sensitivity analysis regarding the values of `r_assumed`
r_assumed <- 0.5
dat_all %>%
  mutate(
    ni = sample_size,
    vi = (dfi / (dfi - 2)) * ((2 * (1 - r_assumed)) / ni) *
      (1 + gi^2 * (ni / (2 * (1 - r_assumed)))) - (gi^2 / ji^2),
    sei = sqrt(vi)
  ) %>%
  filter(!is.na(gi)) %>%
  select(
    article,
    group,
    group_long,
    experiment,
    gender_split,
    gi,
    ni,
    vi,
    sei,
    female_percent,
    age_mean,
    age_sd,
    age_min,
    age_max,
    task
  ) -> dat_all_r

@@

# Create forest plot
dat %>%
  # Make sure the plot will be ordered alphabetically by experiment IDs
  arrange(experiment) %>%
  mutate(
    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
    # Show article labels only for the first experiment per article
    article = if_else(article == lag(article, default = ""), "", article),
    # Compute frequentist confidence intervals
    ci_lb = gi - qnorm(level / 2, lower.tail = FALSE) * sqrt(vi),
    ci_ub = gi + qnorm(level / 2, lower.tail = FALSE) * sqrt(vi),
    ci_print = print_ci(gi, ci_lb, ci_ub)
  ) %>%
  # Prepare plotting canvas
  ggplot(aes(x = gi, y = experiment_f)) +
  geom_vline(xintercept = seq(-3, 3, 1), size = 0.8, color = "grey90") +
  geom_vline(xintercept = seq(-2.5, 2.5, 1), size = 0.4, color = "grey90") +
  # Add article and group labels as text on the left
  geom_text(aes(x = -9.9, label = article), hjust = 0) +
  geom_text(aes(x = -7.1, label = group_long), hjust = 0) +
  # Add experiment-specific effect sizes and CIs as text on the right
  geom_text(aes(x = 3.7, label = print_num(gi)), hjust = 1) +
  geom_text(aes(x = 4.4, label = print_num(ci_lb)), hjust = 1) +
  geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
  # Add Bayesian highest posterior density intervals for each experiment
  stat_interval(aes(x = .epred), draws, point_interval = "mean_hdi") +
  scale_color_grey(
    start = 0.9, end = 0.6,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  # Add experiment-specific effect sizes and CIs as dots with error bars
  geom_errorbar(aes(xmin = ci_lb, xmax = ci_ub)) +
  geom_point(aes(size = ni), shape = 15) + # Or (1 / vi)?
  # Add posterior distribution for the meta-analytic effect
  stat_halfeye(
    aes(x = b_Intercept, y = -1),
    meta_draws,
    point_interval = "mean_hdi"
  ) +
  annotate(
    "text",
    x = c(-9.9, 3.7, 4.4, 5.1),
    y = -0.5,
    label = c(
      "Three-level model",
      print_num(meta_effect_size$Estimate),
      print_num(meta_effect_size$`l-95% CI`),
      print_num(meta_effect_size$`u-95% CI`)
    ),
    hjust = c(0, 1, 1, 1),
    fontface = "bold"
  ) +
  # Add headers for each of the for columns
  annotate( # Just to make the grid lines disappear
    "rect",
    xmin = -Inf,
    xmax = Inf,
    ymin = n_experiments + 0.5,
    ymax = Inf,
    fill = "white"
  ) +
  annotate(
    "text",
    x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
    y = n_experiments + 1.5,
    label = c(
      "Article",
      "Experiment",
      "Effect size plot",
      "Effect size",
      "Lower",
      "Upper"
    ),
    hjust = c(0, 0, 0.5, 1, 1, 1),
    fontface = "bold"
  ) +
  # Styling
  coord_cartesian(ylim = c(-1.5, n_experiments + 2), expand = FALSE) +
  scale_x_continuous(breaks = seq(-3, 3, 0.5)) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    size = "Sample size",
    color = "Bayesian HPDI"
  ) +
  theme_minimal() +
    theme(
      legend.position = "bottom",
      axis.title.x = element_text(hjust = 0.67),
      axis.title.y = element_blank(),
      axis.text.y = element_blank(),
      panel.grid = element_blank(),
      text = element_text(family = "Helvetica")
    )

# Save the plot
ggsave(here(figures_dir, "forest.pdf"), width = 12, height = 14)
```
